Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-22 lineages_18Q3.Rmd
heatmaps: 5 clusterrs (all genes) and CGC genes only

```{r}
make_CRISPRgrob <- function(g) {

@@

```{r}
make_CRISPRlinplot <- function(g) {
  gene <- filter(crispr_data, Hugo_Symbol == g)
  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
  gene <- merge(gene, sig, by = c("Hugo_Symbol", "lineage_name"))
  gene <- mutate(gene, lineage_name = reorder(lineage_name, p, mean))
  crispr_color <- as.character(gene$Color)
  names(crispr_color) <- gene$Mutation_Status
  score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
  round_accuracy <- ifelse(score_range <= 2, 0.25,
                           ifelse(score_range <= 3, 0.5, 1.0))

@@

@@

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/danielc_cell_line_database_completed_extra_SE.tsv", sep = "\t", row.names = NULL, header = TRUE)
colnames(ccl_converter)[4] <- "CCLE_Name"
colnames(ccl_converter)[10] <- "Broad_ID"
```

@@

@@

Make and save heatmap data matrices:
```{r, eval=FALSE}
# Set up heatmap data
chm_scores <- t(crispr)
colnames(chm_scores) <- chm_scores[1, ]
chm_scores <- chm_scores[-1, ]
chm_cols <- colnames(chm_scores)
chm_scores <- apply(chm_scores, 2, as.double)
chm_scores <- apply(chm_scores, 2, function(x) (x - mean(x)) / var(x))
colnames(chm_scores) <- chm_cols
saveRDS(chm_scores, "./data_munging/rds/crispr_heatmap_scores.rds")

@@

Heatmap code:
```{r, eval=FALSE}
chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(-15, 0, 5), c("purple4", "white", "seagreen4")),
        na_col = "black",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_column_names = FALSE,
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_row_names = FALSE,
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)
chm_ge_plot <- Heatmap(chm_ge, name = "Gene Expression (RPKM)",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Gene Expression",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
        width = 1)
chm_cn_plot <- Heatmap(chm_cn, name = "Copy Number",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Copy Number",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
        width = 1)
chm_mut_plot <- Heatmap(chm_mut, name = "Mutation Status",
        col = c("cyan3", "darkorchid"),
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Mutation Status",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
        width = 1)

chm_all_plot <- chm_scores_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot

pdf("./plots_18Q3/crispr_heatmap_all.pdf", width = 100, height = 100, paper = "special") 
draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

@@

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("KRAS")
```

@@

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("TP53")
```

@@

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("BRAF")
```

@@

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("NRAS")
```

@@

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("KRAS")
```

@@

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("TP53")
```

@@

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("BRAF")
```

@@

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("NRAS")
```

>>>>

```{r}
makeCRISPRgrob <- function(g) {

@@

```{r}
makeCRISPRlinplot <- function(g) {
  gene <- filter(crispr_data, Hugo_Symbol == g)
  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
  gene <- merge(gene, sig, by = c("Hugo_Symbol", "lineage_name"))
  gene <- mutate(gene, lineage_name = reorder(lineage_name, p, mean))
  crispr_color <- as.character(gene$Color)
  names(crispr_color) <- gene$Mutation_Status
  score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
  round_accuracy <- ifelse(score_range <= 2, 0.25,
                           ifelse(score_range <= 3, 0.5, 1.0))

@@

### Make individual heatmaps per cluster

Take in a sorted gene list from a larger heatmap and produce smaller, individual heatmaps:
```{r, eval=FALSE}
makeHeatmaps <- function(clust_obj, clust_num) {
  chm_plot_cols <- colnames(clust_obj)
  chm_plot_rows <- rownames(clust_obj)

  chm_plot <- Heatmap(clust_obj, name = "CERES Score",
          bottom_annotation = HeatmapAnnotation(df = chm_annot),
          bottom_annotation_height = unit(5, "in"),
          row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
          col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
          na_col = "black",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          show_column_names = FALSE,
          row_title_gp = gpar(fontsize = 60, fontface = "bold"),
          show_row_names = FALSE,
          row_dend_reorder = TRUE,
          column_dend_reorder = TRUE,
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          column_dend_height = unit(4, "in"),
          row_dend_width = unit(4, "in"),
          width = 3)

  chm_ge_plot <- Heatmap(chm_ge[row_order(chm_scores_draw)[[clust_num]],], name = "Gene Expression (RPKM)",
          col = colorRamp2(c(min(chm_ge[!is.na(chm_ge)]), 0.25, max(chm_ge[!is.na(chm_ge)])), c("dodgerblue4", "white", "firebrick4")),
          na_col = "black",
          cluster_rows = FALSE, cluster_columns = FALSE,
          show_row_names = FALSE, show_column_names = FALSE,
          column_title = "Gene Expression",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          width = 1)
  chm_cn_plot <- Heatmap(chm_cn[row_order(chm_scores_draw)[[clust_num]],], name = "Copy Number",
          col = colorRamp2(c(min(chm_cn[!is.na(chm_cn)]), 2, max(chm_cn[!is.na(chm_cn)])), c("dodgerblue4", "white", "firebrick4")),
          na_col = "black",
          cluster_rows = FALSE, cluster_columns = FALSE,
          show_row_names = FALSE, show_column_names = FALSE,
          column_title = "Copy Number",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          width = 1)
  chm_mut_plot <- Heatmap(chm_mut[row_order(chm_scores_draw)[[clust_num]],], name = "Mutation Status",
          na_col = "black",
          col = c("cyan3", "darkorchid"),
          cluster_rows = FALSE, cluster_columns = FALSE,
          show_row_names = FALSE, show_column_names = FALSE,
          column_title = "Mutation Status",
          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
          column_order = chm_plot_cols,
          row_order = chm_plot_rows,
          width = 1)

  chm_all_plot <- chm_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot

  pdf(paste0("./plots_18Q3/crispr_heatmap_all_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
  draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()

  pdf(paste0("./plots_18Q3/crispr_heatmap_ge_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
  draw(chm_plot + chm_ge_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()

  pdf(paste0("./plots_18Q3/crispr_heatmap_mut_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
  draw(chm_plot + chm_mut_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()

  pdf(paste0("./plots_18Q3/crispr_heatmap_cn_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
  draw(chm_plot + chm_cn_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
  seekViewport("annotation_Cell_Line_SSMD")
  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Cas9_Activity")
  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Culture_Type")
  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Tissue")
  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Primary_Disease")
  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Gender")
  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  seekViewport("annotation_Source")
  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
  dev.off()
}
```

@@

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
```

@@

## Cancer Gene Census (CGC) gene list

Select genes from the Cancer Gene Census (CGC). The list was pulled from the [International Cancer Genome Consortium (ICGC) data portal](https://dcc.icgc.org/search/g?filters=%7B%22gene%22:%7B%22curatedSetId%22:%7B%22is%22:%5B%22GS1%22%5D%7D%7D%7D) (Advaced Search > Genes > Curated Gene Set > Cancer Gene Census).
```{r}
cgc <- data_frame("Hugo_Symbol" = read.delim("./data_munging/gene-ids-for-set-Cancer Gene Census.tsv", header = FALSE, sep = "\t")[, 2])
```

@@

### Data management

Make and save heatmap data matrices:
```{r, eval=FALSE}
# Set up heatmap data
chm_scores <- t(crispr)
colnames(chm_scores) <- chm_scores[1, ]
chm_scores <- chm_scores[-1, ]
chm_rows <- rownames(chm_scores)
chm_cols <- colnames(chm_scores)
chm_scores <- apply(chm_scores, 2, as.double)
chm_scores <- apply(chm_scores, 2, function(x) (x - mean(x)) / var(x))
colnames(chm_scores) <- chm_cols
rownames(chm_scores) <- chm_rows
saveRDS(chm_scores, "./data_munging/rds/crispr_heatmap_scores.rds")

@@

### K-means clustered

Code for k-means clustered heatmap:
```{r, eval=FALSE}
chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_column_names = FALSE,
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_row_names = FALSE,
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3,
        km = 5, gap = unit(0.5, "in"))

chm_scores_draw <- draw(chm_scores_plot, heatmap_legend_side = "right", annotation_legend_side = "right")

pdf("./plots_18Q3/crispr_heatmap_euclidean_split5.pdf", width = 100, height = 100, paper = "special")
chm_scores_draw
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()

# chm_scores_c1 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[1]],])))
# chm_scores_c2 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[2]],])))
# chm_scores_c3 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[3]],])))
# chm_scores_c4 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[4]],])))

chm_scores_c1 <- chm_scores[row_order(chm_scores_draw)[[1]],]
chm_scores_c2 <- chm_scores[row_order(chm_scores_draw)[[2]],]
chm_scores_c3 <- chm_scores[row_order(chm_scores_draw)[[3]],]
chm_scores_c4 <- chm_scores[row_order(chm_scores_draw)[[4]],]
chm_scores_c5 <- chm_scores[row_order(chm_scores_draw)[[5]],]

makeHeatmaps(chm_scores_c1, 1)
makeHeatmaps(chm_scores_c2, 2)
makeHeatmaps(chm_scores_c3, 3)
makeHeatmaps(chm_scores_c4, 4)
makeHeatmaps(chm_scores_c5, 5)
```

### CGC genes

Code for heatmap of CGC-filtered genes only:
```{r, eval=FALSE}
chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)

chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
        bottom_annotation = HeatmapAnnotation(df = chm_annot),
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        row_names_gp = gpar(fontsize = 10),
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_names_gp = gpar(fontsize = 10),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

chm_plot_cgc_cols <- colnames(chm_scores_cgc)[unlist(column_order(chm_plot_cgc))]
chm_plot_cgc_rows <- rownames(chm_scores_cgc)[unlist(row_order(chm_plot_cgc))]

chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression (RPKM)",
        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0.25, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
        na_col = "black",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Gene Expression",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = chm_plot_cgc_cols,
        row_order = chm_plot_cgc_rows,
        width = 1)
chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 2, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("dodgerblue4", "white", "firebrick4")),
        na_col = "black",
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Copy Number",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = chm_plot_cgc_cols,
        row_order = chm_plot_cgc_rows,
        width = 1)
chm_mut_plot_cgc <- Heatmap(chm_mut_cgc, name = "Mutation Status",
        na_col = "black",
        col = c("cyan3", "darkorchid"),
        cluster_rows = FALSE, cluster_columns = FALSE,
        show_row_names = FALSE, show_column_names = FALSE,
        column_title = "Mutation Status",
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        column_order = chm_plot_cgc_cols,
        row_order = chm_plot_cgc_rows,
        width = 1)

chm_all_plot_cgc <- chm_plot_cgc + chm_ge_plot_cgc + chm_cn_plot_cgc + chm_mut_plot_cgc

pdf("./plots_18Q3/crispr_heatmap_all_cgc.pdf", width = 100, height = 100, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

@@

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("KRAS")
```

@@

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("TP53")
```

@@

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("BRAF")
```

@@

```{r fig.height=12, fig.width=12}
makeCRISPRgrob("NRAS")
```

@@

```{r fig.height=10, fig.width=15}
makeCRISPRlinplot("KRAS")
```

@@

```{r fig.height=10, fig.width=15}
makeCRISPRlinplot("TP53")
```

@@

```{r fig.height=10, fig.width=15}
makeCRISPRlinplot("BRAF")
```

@@

```{r fig.height=10, fig.width=15}
makeCRISPRlinplot("NRAS")
```
